A Kochen-Specker system has at least 22 vertices

### 2014-04-08 main.tex
Also for email adresses
Add attributions and amsthm
Improve abstract

\usepackage{authblk}

@@

% TODO will we keep these @cs.ru.nl addresses?
\affil{Institute for Computing and Information Sciences\\
       Radboud Universiteit Nijmegen\\
   \{\texttt{bwesterb},\texttt{suijlen}\}\texttt{@cs.ru.nl}}

@@

\begin{abstract}
    A Kochen-Specker system is a set of points on the sphere,
    such that there is no~$\{0,1\}$-coloring such that
    at most one of two orthogonal points is assigned~$1$
    and of three pairwise orthogonal points exactly one
    is assigned~$1$.
    The existence of such a system is the basis of the Kochen-Specker
    and Free Will theorems.  At the time of writing, the smallest known
    KS system has 31 vectors.

    Arends, Ouaknine and Wampler have shown that a KS system has at least
    18 vectors, by reducing the problem to the existence of graphs
    with a certain topological embeddability and non-colorability property.
    Deciding embeddability and the sheer number of graphs on more than~$17$
    vertices, proved the bottleneck in their search.

@@

\section{Introduction}
TODO

@@

\bibliography{main}{}
\bibliographystyle{plain}

>>>>

\usepackage{paralist}
\usepackage{authblk}
\usepackage{amsthm}

\newcounter{main}
\newtheorem{prop}[main]{Proposition}
\newtheorem{thm}[main]{Theorem}
\newtheorem{lem}[main]{Lemma}
\theoremstyle{definition}
\newtheorem{dfn}[main]{Definition}
\theoremstyle{remark}
\newtheorem{rem}[main]{Remark}

@@

% TODO will we keep these @cs.ru.nl addresses?
\affil{Institute for Computing and Information Sciences\\
       Radboud Universiteit Nijmegen\\
   \{\texttt{suijlen},\texttt{bwesterb}\}\texttt{@cs.ru.nl}}

@@

\begin{abstract}
    At the heart of the Conway's Free Will theorems and Kochen-Specker's
        argument
    is the existence of a Kochen-Specker (KS) system:
    a set of points on the sphere,
    that has no~$\{0,1\}$-coloring such that
    at most one of two orthogonal points are colored~$1$
    and of three pairwise orthogonal points exactly one
    is colored~$1$.
    In public lectures, Conway encouraged the search for small
    KS systems.  
    At the time of writing, the smallest known
    KS system has 31 vectors.

    Arends, Ouaknine and Wampler have shown that a KS system has at least
    18 vectors, by reducing the problem to the existence of graphs
    with a topological embeddability and non-colorability property.
    Deciding embeddability and the sheer number of graphs on more than~$17$
    vertices, proved the bottleneck in their search.

@@

\section{Introduction}

% TODO whose idea is this orthogonality graph
TODO

@@

\section{Acknowledgments}
We wish to thank the following for their generous contribution to the
distributed computation:
    the Digital Security group, Intelligent Systems group
    and the C\&CZ service of the Radboud University;
    Wouter Geraedts and
    Jille Timmermans.

% attribute mckay for answering questions?
\bibliography{main}{}
\bibliographystyle{plain}
